### 2016-10-05 Paper_v8.tex
Updates for the rebuttal

We identified model subpopulations that exhibited different behaviors following exposure to TGF$-\beta$1/2 (Fig. \ref{fg:F3}B).
Analysis of the molecular signatures of these subpopulations suggested the abundance, localization and state of the Sp1, AP-1 and NFATc transcription factors controlled population heterogeneity.
The majority of models ($>$80\%) responded to treatment, moving away from the untreated population (Fig \ref{fg:F3}A-F, gray).
These models showed the classically expected behavior, a switch from an epithelial to mesenchymal phenotype following TGF$-\beta$1/2 exposure.
Some models resembled untreated cells; they had elevated phosphorylated Sp1, relative to non-induced cells,
which decreased E-cadherin expression through Slug-mediated inhibition, which in turn increased Vimentin expression through TGF$-\beta$3 autocrine signaling and the liberation of $\beta$-catenin. However, the most biologically interesting behavior was exhibited by cells achieving a hybrid phenotype, most notable in a dual treatment condition (\ref{fg:F3}C, black arrow), but also present in a small percentage of untreated cells (Fig. \ref{fg:F3}B, gray arrow).
Models with this hybrid phenotype had elevated Sp1 and NFAT transcriptional activity, resulting in simultaneously increased Vimentin and E-cadherin expression (Fig. \ref{fg:F4}A).

@@

\begin{figure}
\includegraphics [width=1.0\linewidth] {./figs/Fig2_training.pdf}
\caption{Training and validation simulations. The population of EMT models qualitatively captured TGF$-\beta$-induced EMT signaling.
(A-I) The population was generated using JuPOETs and trained using 11 different objective functions (41 data sets) taken from Medici \emph{et al.} \cite{Medici:2008fk}.
The model captured the simulated experiments for all cases when compared to randomized controls.
(J-L)  The model populations were also compared against untrained temporal data to measure the effectiveness as a pure prediction.}\label{fg:F2}
\end{figure}

>>>>

We identified model subpopulations that exhibited different behaviors following exposure to TGF$-\beta$1/2 (Fig. \ref{fg:F3}B).
Analysis of the molecular signatures of these subpopulations suggested the abundance, localization and state of the Sp1, AP-1 and NFATc transcription factors controlled population heterogeneity.
The majority of models ($>$80\%) responded to treatment, moving away from the untreated population (Fig \ref{fg:F3}A-F, gray).
These models showed the classically expected behavior, a switch from an epithelial to mesenchymal phenotype following TGF$-\beta$1/2 exposure.
Some models resembled untreated cells; they had elevated phosphorylated Sp1, relative to non-induced cells,
which decreased E-cadherin expression through Slug-mediated inhibition, which in turn increased Vimentin expression through TGF$-\beta$3 autocrine signaling and the liberation of $\beta$-catenin. However, the most biologically interesting behavior was exhibited by cells achieving a hybrid phenotype, most notable in a dual treatment condition (\ref{fg:F3}C, black arrow), but also present in a small percentage of untreated cells (Fig. \ref{fg:F3}B, gray arrow).
Models with this hybrid phenotype had elevated Sp1 and NFAT transcriptional activity, resulting in simultaneously increased Vimentin and E-cadherin expression (Fig. \ref{fg:F4}A).
However, these conclusions are likely sensitivity to the components that we have included in the model, and could also involve proteins that we have not considered.

@@

\begin{figure}
\includegraphics [width=1.0\linewidth] {./figs/Fig2_training.pdf}
\caption{Training and validation simulations. The population of EMT models qualitatively captured TGF$-\beta$-induced EMT signaling.
(A-I) The population was generated using JuPOETs and trained using 11 different objective functions (41 data sets) taken from Medici \emph{et al.} \cite{Medici:2008fk}.
The model captured the simulated experiments for all cases when compared to randomized controls.
(J-L)  The model populations were also compared against untrained temporal data to measure the effectiveness as a pure prediction.
The western blot data was reproduced from Medici \emph{et al.} \cite{Medici:2008fk}. The intensity of each band was estimated using the ImageJ program.
These blot intensities were then used as the training data for the EMT parameter estimation studies. }\label{fg:F2}
\end{figure}
